Optimal Fitting of Planar Curves to Prescribed Constraints

### 2014-01-21 idp/documentation/paper.tex
fixed a few mistakes in the definitions section

			A few basic definitions about vectors in the euclidean plane are needed:
			\begin{align*}
				\overline{\cdot} & : \function{\R{2}}{\R{2}} & \overline{v}      & = \vectorB{-v_2}{v_1}      && \text{orthogonal vector}\\
				\alpha           & : \function{\R{2}}{\RR} i & \apply{\alpha}{v} & = \apply{\atan2}{v_2, v_1} && \text{polar coordinate angle}
			\end{align*}

@@

			Parametric curves are functions \(\phi : \function{\unit}{\R{n}}\), called the parametrization function. The represented curve is then the list of points that are traversed by this function. While there are many ways to parametrize a given curve, that is, represent it using a parametrization function, we are usually interested in those which yield a sufficiently smooth parametrization function, allowing for the concise description of curve properties using differential geometry.

@@

			Using these definitions, the direction \(\apply{\delta}{t}\) is equal to the tangent angle at the point \(\apply{\phi}{t}\). If the curve is locally a straight line at the point \(\apply{\phi}{t}\), the curvature \(\apply{\chi}{t}\) is equal to \(0\). Otherwise, the curvature \(\apply{\chi}{t}\) is equal (up to sign) to the inverse the radius of the osculating circle at the point \(\apply{\phi}{t}\).

@@

			One may notice that this notion of continuity is a little too strict. A curve may be arbitrarily smooth, while its parametrization does not even have \(\contp{1}\) continuity, since the derivatives of the parametrization function may have discontinuities that do not manifest themselves in the curve that they represent. If that is the case, one can always find a different parametrization of the same curve that does not have these discontinuities. This insight gives rise to the definition of geometric continuity, denoted by \(\contg{n}\), which only requires that there exists a reparametrization of the parametric curve which is \(\contp{n}\) continuous.

>>>>

			A few basic definitions about vectors in the euclidean plane are needed:
			\begin{align*}
				\overline{\cdot} & : \function{\R{2}}{\R{2}} & \overline{v}      & = \vectorB{-v_2}{v_1}      && \text{orthogonal vector}\\
				\alpha           & : \function{\R{2}}{\RR}   & \apply{\alpha}{v} & = \apply{\atan2}{v_2, v_1} && \text{polar coordinate angle}
			\end{align*}

@@

			Parametric curves are described using functions \(\phi : \function{\unit}{\R{n}}\), called the parametrization function. The represented curve is then the image of this function. While there are many ways to parametrize a given curve, that is, represent it using a parametrization function, we are usually interested in those which yield a sufficiently smooth parametrization function, allowing for the concise description of curve properties using differential geometry.

@@

			Using these definitions, the direction \(\apply{\delta}{t}\) is equal to the tangent angle at the point \(\apply{\phi}{t}\). If the curve is locally a straight line at the point \(\apply{\phi}{t}\), the curvature \(\apply{\chi}{t}\) is equal to \(0\). Otherwise, the curvature \(\apply{\chi}{t}\) is equal (up to sign) to the inverse of the radius of the osculating circle at the point \(\apply{\phi}{t}\).

@@

			One may notice that this notion of continuity is a little too strict. A curve may look arbitrarily smooth, while its parametrization does not even have \(\contp{1}\) continuity, since the derivatives of the parametrization function may have discontinuities that do not manifest themselves in the curve that they represent. If that is the case, one can always find a different parametrization of the same curve that does not have these discontinuities. This insight gives rise to the definition of geometric continuity, denoted by \(\contg{n}\), which only requires that there exists a reparametrization of the parametric curve which is \(\contp{n}\) continuous.
